---
title: "US CHINA TRADE"
author: "PEIZHI ZHANG, Hanyi Wang, Xinyi Shi, Huiling Zhou"
date: "2023-04-27"
output: html_document

---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r, message = FALSE, warning = FALSE, error=FALSE, echo=FALSE}

library(shiny)
library(leaflet)
library(readr)
library(dplyr)
library(tidyr)
library(stringr)
library(RCurl)
library(sqldf)
library(plotly)
library(leaflet)
library(leaflet.extras)
library(ggplot2)
library(tm)
library(scales)
library(DT)
library(tidyverse)
library(ggrepel)
library(readr)
library(data.table)
library(tm)
library(SnowballC)
library(wordcloud)
library(tidytext)
library(tidyverse)
library(readxl)
library(tidyverse)
library(dplyr)
library(shiny)
library(ggplot2)
library(tidyr)
library(readr)
library(cowplot)
library(Cairo)

```

### Value and Quantity of Trade Balance of Photovoltaic Products between China and US

```{r, message = FALSE, warning = FALSE, error=FALSE, echo=FALSE}

CN_US_cleaned_all <- read.csv("~/Downloads/CN_US_cleaned_all.csv")

subset <- CN_US_cleaned_all[grep("^8541", CN_US_cleaned_all$HS6code),]


plot_data <- subset %>%
  group_by(period) %>%
  summarise(total_balance_primaryvalue = sum(balance_primaryValue),
            total_balance_qty = sum(balance_qty)) %>%
  mutate(primary_value_label = paste("Period: ", period, "<br> Balance Primary Value: ",
                                     round(total_balance_primaryvalue*10^(-3),2), " (thousands USD)"),
         qty_label = paste("Period: ", period, "<br> Balance Quantity: ",
                            round(total_balance_qty*10^(-4), 2), " (ten thousands units)"))

plot1 <- ggplot(plot_data, aes(x = period)) +
  geom_line(aes(y = total_balance_primaryvalue*10^(-3), color = "Total Balance Primary Value (thousands USD)"), size = 1.5) +
  geom_point(aes(y = total_balance_primaryvalue*10^(-3), color = "Total Balance Primary Value (thousands USD)", text = primary_value_label), size = 3) +
  geom_line(aes(y = total_balance_qty*10^(-4), color = "Total Balance Quantity (ten thousands units)"), size = 1.5) +
  geom_point(aes(y = total_balance_qty*10^(-4), color = "Total Balance Quantity (ten thousands units)", text = qty_label), size = 3) +
  scale_color_manual(values = c("green", "blue")) +
  scale_y_continuous(name = "Total Balance", labels = scales::comma) +
  labs(x = "Year", y = "Total balance primary value (thousands USD)") +
  ggtitle("China vs. US: Balance Primary Value and Quantity per Year(2017-21)") +
  theme_minimal() +
  theme(axis.title = element_text(size = 16),
        plot.title = element_text(size = 18),
        panel.grid.major = element_line(color = "gray", linetype = "dashed"),
        legend.position = "bottom",
        legend.direction = "vertical") +
  labs(caption = "Source: CN_US_cleaned_all dataset")
  

plotly_fig <- ggplotly(plot1, tooltip = c("text"), colors = c("Total Balance Primary Value (thousands USD)" = "green", "Total Balance Quantity (ten thousands units)" = "blue"))

plotly_fig <- plotly_fig %>% layout(legend = list(x = 0.2, y = -0.5))

plotly_fig <- plotly_fig %>% layout(title = list(text = "China vs. US: Balance Primary Value and Quantity per Year(2017-21)", font = list(size = 15)))

plotly_fig


```

## China's export to the Southeast Asian countries

As more countries invest in solar infrastructure, they are competing to gain an advantage in the market. However, this competition has caused trade disputes between countries, particularly China and the United States. One major issue is the accusation that Chinese manufacturers are selling their solar products at unfairly low prices, which has led to the US imposing tariffs. As a result, Chinese manufacturers have moved their operations to Southeast Asia and continue to export to the US. These factories often rely on raw materials from China, like polysilicon.

There is an interactive bar chart that shows China's exports of silicon and photovoltaic cells to three Southeast Asian countries identified by the US, as well as to the US itself. By selecting "Photovoltaic cells (Downstream)", we can see that China had a high trade surplus with the US, but this changed drastically in 2018, potentially due to the US-China Trade War launched in 2017. The surplus increased steadily from 2019-2021 as the US still relied heavily on China's exports. However, in 2022, another investigation was launched on China's solar manufacturing, which caused a contraction in China's direct exports to the US. Along with this contraction, China's exports to Malaysia, Cambodia, and Thailand increased, reflecting the idea that China is transferring its solar exports to third-party countries before sending them to the US.



```{r, message = FALSE, warning = FALSE, error=FALSE, echo=FALSE}

filtered_data_CN_solar <- read.csv("~/Documents/filtered_data_CN_solar.csv")
Partner_codes <- read.csv("~/Documents/partnerAreas.csv")
US_solar <- read.csv("~/Documents/US_Solar_imports.csv")

Partner_codes <- read.csv("~/Documents/partnerAreas.csv") %>% 
  rename(partnerCode = id, partnerCountry = text) %>% 
  mutate(partnerCode = as.factor(partnerCode),
         partnerCountry = as.factor(partnerCountry))


merged_data <- merge(filtered_data_CN_solar, Partner_codes, by = "partnerCode", all.x = TRUE)
merged_data <- merged_data %>% 
  mutate(category = case_when(
    HS6code %in% c("854150", "854140") ~ "Photovoltaic cells (Downstream)",
    HS6code %in% c("391000", "280461", "280469") ~ "Silicon (Upstream)",
    TRUE ~ ""
  ))
merged_data$balance_primaryValue <- merged_data$balance_primaryValue / 1000000
# UI
ui <- fluidPage(
  titlePanel("China's Solar Panels Trade Balance"),
  sidebarLayout(
    sidebarPanel(
      selectInput("year", "Year:",
                  choices = c("2017", "2018", "2019", "2020", "2021")),
      selectInput("category", "Solar panel value chain:",
                  choices = c("Silicon (Upstream)", "Photovoltaic cells (Downstream)"))
    ),
    mainPanel(
      plotOutput("plot", height = "500px")
    )
  )
)
# Server
server <- function(input, output) {
  
  # Filter the data based on the selected year and category
  filtered_data <- reactive({
    subset_data <- subset(merged_data, partnerCountry %in% c("Cambodia", "Malaysia", "Thailand", "Vietnam", "USA"))
    filtered_data <- subset_data %>% 
      filter(period == input$year) %>% 
      filter(category == input$category) %>% 
      group_by(period, partnerCountry) %>% 
      summarize(balance_primaryValue = sum(balance_primaryValue))
    return(filtered_data)
  })
  
  # Create a bar chart
  output$plot <- renderPlot({
    ggplot(filtered_data(), aes(x = partnerCountry, y = balance_primaryValue, fill = partnerCountry)) +
      geom_col(position = "stack") +
      labs(title = "Solar panel value chain trade Balance with China",
           x = "Partner Country",
           y = "Trade Balance with China (million USD)")+
      scale_fill_brewer(palette = "Blues")
  })
}

# Run the app
shinyApp(ui, server)
```


To further strengthen our previous assumption, we obtained import data on photovoltaic cells from the United States from the past four years. We identified the top five countries that export solar panels to the United States. China had been the top exporter until last year when stricter export regulations were imposed. Surprisingly, Mexico has now taken the lead. This may be due to the tariffs that the United States placed on Southeast Asian countries, which has prompted the trend of exporting solar panels to Mexico as a third-party country.


```{r, message = FALSE, warning = FALSE, error=FALSE, echo=FALSE}

##Graphic two##
##Cleaning U.S. solar data
US_solar_cleaned <- US_solar %>%
  rename(HS6code = CmdCode) %>% 
  mutate(HS6code = as.factor(HS6code),
         FlowCode = as.factor(FlowCode),
         PartnerCode = as.factor(PartnerCode),
         ReporterCode = as.factor(ReporterCode)) %>%
  # Select data columns to keep
  select(Period, ReporterCode, # Year and reporting country
         PartnerCode, Partner2Code, # Trading partner(s)
         FlowCode, # Import / Export
         HS6code, # Commodity HS code
         Qty, QtyUnitCode, NetWgt, # Quantity traded and units of commodity, net weight
         PrimaryValue) %>% # Combination between FOB and CIF values 
  # Group all export/import observations for each partner country in the same rows
  group_by(Period, ReporterCode, PartnerCode, HS6code, QtyUnitCode, FlowCode) %>%
  summarise(Qty=sum(Qty), NetWgt=sum(NetWgt), PrimaryValue=sum(PrimaryValue)) %>%
  ungroup() %>%
  pivot_wider(id_cols = c("Period","ReporterCode","PartnerCode","HS6code","QtyUnitCode"), 
              names_from = c("FlowCode"),
              values_from = c("Qty","PrimaryValue","NetWgt")) %>% 
  replace(is.na(.), 0) %>% 
  mutate(balance_primaryValue = PrimaryValue_X - PrimaryValue_M,
         balance_qty = Qty_X - Qty_M,
         balance_netWgt = NetWgt_X - NetWgt_M) %>% 
  arrange(HS6code, desc(balance_primaryValue))
Partner_codes_P <-  read.csv("~/Documents/partnerAreas.csv") %>% 
  rename(PartnerCode = id, PartnerCountry = text) %>% 
  mutate(PartnerCode = as.factor(PartnerCode),
         PartnerCountry = as.factor(PartnerCountry))
merged_data_US <- merge(US_solar_cleaned, Partner_codes_P, by = "PartnerCode", all.x = TRUE)
merged_data_US_grouped <- merged_data_US %>%
  group_by(PartnerCountry, Period) %>%
  summarize(total_balance_primaryValue = sum(balance_primaryValue)) %>%
  ungroup()
  
top_countries <- merged_data_US_grouped[order(-merged_data_US_grouped$total_balance_primaryValue),]
top_countries_list <- lapply(sort(unique(top_countries$Period), decreasing = FALSE), function(x) {
  top_5 <- head(subset(top_countries, Period == x), 5)
  top_5$PartnerCountry[top_5$PartnerCountry == "China, Hong Kong SAR"] <- "China"
  top_5$PartnerCountry <- factor(top_5$PartnerCountry, levels = unique(top_5$PartnerCountry))
  top_5$total_balance_primaryValue <- top_5$total_balance_primaryValue / 1000000 # Divide by 1 million to display in millions
  return(top_5)
})
##
plot_list <- lapply(top_countries_list, function(df) {
  # Set the color based on whether the country is China or not
  df$color <- ifelse(df$PartnerCountry == "China", "#1F4788", "#80ADD7")
  
  # Create the bar chart
  ggplot(df, aes(x = total_balance_primaryValue, y = PartnerCountry, fill = color)) +
    geom_bar(stat = "identity", width = 0.4) +
    scale_fill_identity() +
    labs(x = NULL, y = NULL, title = paste(unique(df$Period))) +
    theme_minimal() +
    theme(plot.title = element_text(hjust = 0.1, size = 8, face = "bold"),
          legend.position = "none",
          panel.grid.major.y = element_blank(),
          panel.grid.major.x = element_blank())+
    scale_x_continuous(limits = c(0, 450), breaks = seq(0, 400, by = 200))+
    scale_y_discrete(limits = rev(levels(df$PartnerCountry)))+
    coord_fixed(ratio = 100)
})
plot_grid(plotlist = plot_list, ncol = 4, align = "h") %>%
  ggdraw() +
  draw_label("The United States Top 5 Solar Panel Import Countries", fontface = "bold", x = 0.5, y = 0.7)


```
```{r, message = FALSE, warning = FALSE, error=FALSE, echo=FALSE}

tradedata <- read.csv("~/Documents/tradedata.csv", sep="")

```
```{r, message = FALSE, warning = FALSE, error=FALSE, echo=FALSE}


new_stops <- c("room","one","stop","minutes","nearby","listing","br","equipped","building","just","can","size","prior","welcome","ave","away","will","aside","except","month","home","bedroom","bathroom","two","three","apartment","unit","area","'ll","place","located","blocks","couple","plus","restaurants","shops","must","like","surrounded","daily","will","provide","without","within","spacebbr","bthe","nycbr","nyc","years","looking","information","give","makes","street","ny","city","quite","come","also","likebr","people","giving","five","behind","need","allow","space","next","world","stay","single","kitchen","guest","ride","min","citi","cit", "cinemat", "cinco", "chunk","circl","access","accessbbr","accomodation","accomod","air","amaz","footnote","citation","moreover","beside","on","also","including","if","article","then","likely","such","as","requires", "Chinese", "youre", "present", "past", "Chinas", "China's", "India", "number", "Maria", "Although", "studies","solar","energy","hence","third","section","study",
               "yesterday","comes","thank","earlier","came","doc","talk","tell","found","part","way",
               "thats","therefore","energies","yet","morning","done","theyre","bri","suggests","lets",
               "taking","believe","job","Chinese","China","trade", "think","know","much",
               "said","however","second","thus","country", "china", "market","industry","United","States","chinese","countries",
               stopwords("en"))

data_corpus <- VCorpus(VectorSource(tradedata$text))
data_corpus <- tm_map(data_corpus, removePunctuation)
data_corpus <- tm_map(data_corpus, content_transformer(tolower))
data_corpus <- tm_map(data_corpus, stripWhitespace)
data_corpus <- tm_map(data_corpus, removeWords, stopwords("english"))
data_corpus <- tm_map(data_corpus, removeWords, c(new_stops))
data_corpus <- tm_map(data_corpus, removeNumbers)

```

## Word Cloud of Solar Panel Trade from Journal Articles

The text analysis visualizes the most frequently used words in 50 journals on solar panel trade between China and the US. We can see that in most of these documents, the keywords are “growth”, “power”, “economic”, “domestic”, “exports”, “government support”, “technology”, “environmental”, “investment”, “subsidies”, and so on. There are many frequently appeared themes from these terms, along with the context of the US and China trade war currently taking place. For instance, “growth” likely refers to the expansion of the solar panel industry in both China and the US, and the potential for further growth in the future. “Power” could refer to a number of things, including the use of solar power as a renewable energy source, the economic and political power of China and the US in the global solar panel industry, or the potential for solar power to empower individuals and communities by providing access to energy.”Economic” may refer to the economic benefits and impacts of the solar panel trade between China and the US, including job creation, economic growth, and the potential for new markets and industries to emerge. “Domestic” may suggest that the production and consumption of solar panels within each country's domestic market, as well as the potential for domestic policies and regulations to impact the solar panel trade between China and the US. “Exports” could mean the export of solar panels from China to the US, and the potential for this trade to drive economic growth and create jobs in both countries. “Government support” might refer to the role of government policies, regulations, and subsidies in supporting the solar panel industry in both China and the US. “Technology” refers to the technological advancements and innovations driving the solar panel industry, as well as the potential for new technologies to emerge in the future. “Environmental” likely refers to the environmental benefits and impacts of the solar panel industry, including the reduction of greenhouse gas emissions and the potential for solar power to mitigate climate change. “Investment” refers to the investments being made in the solar panel industry by companies, governments, and individuals, as well as the potential for future investments to drive growth and innovation in this industry. “Subsidies” suggests the subsidies provided by governments to support the production and consumption of solar panels, as well as the potential for these subsidies to impact the competitiveness of the solar panel industry in different markets.




```{r, message = FALSE, warning = FALSE, error=FALSE, echo=FALSE}

dtm <- DocumentTermMatrix(data_corpus)

word_freq <- colSums(as.matrix(dtm))

word_freq_df <- data.frame(word = names(word_freq), freq = word_freq)

wordcloud(words = word_freq_df$word, freq = word_freq_df$freq, min.freq = 5, max.words = 200,
          colors=c("green","blue"))

```


## Solar Energy Research Database




```{r, message = FALSE, warning = FALSE, error=FALSE, echo=FALSE}

df <- read_excel("~/Documents/1645011.xlsx")

# Define UI for application that draws a histogram
ui <- fluidPage(
  
  # Application title
  titlePanel("Solar Energy Research Database"),
  
  sidebarLayout(
    sidebarPanel(
      checkboxGroupInput(
        inputId = "SUBPROGRAM",
        label = "PROGRAM AREA",
        choices = c("Concentrating Solar Power" = "Concentrating Solar Power",
                    "Manufacturing and Competitiveness" = "Manufacturing and Competitiveness",
                    "Photovoltaics" = "Photovoltaics", 
                    "Soft Costs" = "Soft Costs",
                    "Systems Integration" = "Systems Integration"
					),
        selected = c("Concentrating Solar Power",
                     "Manufacturing and Competitiveness",
                     "Photovoltaics", 
                     "Soft Costs",
                     "Systems Integration"
        ),
		),
	
      selectInput(
        inputId = "Status",
        label = "STATUS",
    		choices = c("Any" = "Any",
    		            "Active" = "Active",
                    "Inactive" = "Inactive"
					),
        selected = "Any"
      ),
	  
      selectInput(
        inputId = "FOA_Acronym",
        label = "FUNDING OPPORTUNITY",
        choices = c("All" = "All",
                    "AOP" = "AOP",
                    "AOP 13-15" = "AOP 13-15",
                    "AOP 2015" = "AOP 2015",
                    "AOP 2016" = "AOP 2016",
                    "ASSIST" = "ASSIST",
                    "Bos-X" = "Bos-X",
                    "BRIDGE" = "BRIDGE",
                    "BTMS" = "BTMS",
                    "CSP 2012 Lab Call" = "CSP 2012 Lab Call",
                    "CSP APOLLO" = "CSP APOLLO",
                    "CSP ARRA" = "CSP ARRA",
                    "CSP Baseload" = "CSP Baseload",
                    "CSP COLLECTS" = "CSP COLLECTS",
                    "CSP HIBRED" = "CSP HIBRED",
                    "CSP Lab Call" = "CSP Lab Call",
                    "CSP R&D" = "CSP R&D",
                    "CSP SunShot R&D" = "CSP SunShot R&D",
                    "Desal" = "Desal",
                    "DISTANCE" = "DISTANCE",
                    "DuraMat" = "DuraMat",
                    "ELEMENTS" = "ELEMENTS",
                    "EMPOWERED" = "EMPOWERED",
                    "ENERGISE" = "ENERGISE",
                    "Engineering Research Centers" = "Engineering Research Centers",
                    "Forecasting 2" = "Forecasting 2",
                    "F-PACE" = "F-PACE",
                    "F-PACE 2" = "F-PACE 2",
                    "FY20 PVSK" = "FY20 PVSK",
                    "FY21 PV & CSP" = "FY21 PV & CSP",
                    "FY21 SI & Incubator" = "FY21 SI & Incubator",
                    "FY22 CSP" = "FY22 CSP",
                    "FY22 SIPS - CSP & PV" = "FY22 SIPS - CSP & PV",
                    "GEARED" = "GEARED",
                    "Gen3 CSP" = "Gen3 CSP",
                    "Gen3 CSP Lab Call" = "Gen3 CSP Lab Call",
                    "General AOP" = "General AOP",
                    "GMLC-GM" = "GMLC-GM",
                    "GMLC-RDS" = "GMLC-RDS",
                    "High Pen" = "High Pen",
                    "Incubator 1" = "Incubator 1",
                    "Incubator 2" = "Incubator 2",
                    "Incubator 3" = "Incubator 3",
                    "Incubator 4" = "Incubator 4",
                    "Incubator 5" = "Incubator 5",
                    "Incubator 6" = "Incubator 6",
                    "Incubator 7" = "Incubator 7",
                    "Incubator 8" = "Incubator 8",
                    "Incubator 9" = "Incubator 9",
                    "Innovative Pathways" = "Innovative Pathways",
                    "JIT" = "JIT",
                    "Lab Call 19-21" = "Lab Call 19-21",
                    "Lab Call FY20" = "Lab Call FY20",
                    "Lab Call FY21" = "Lab Call FY21",
                    "Lab Call FY22-24" = "Lab Call FY22-24",
                    "Lab Core FY21" = "Lab Core FY21",
                    "Mini-SuNLaMP" = "Mini-SuNLaMP",
                    "MURA" = "MURA",
                    "MURI" = "MURI",
                    "NextGen 2" = "NextGen 2",
                    "NextGen 3" = "NextGen 4",
                    "Orange Button" = "Orange Button",
                    "Plug and Play" = "Plug and Play", 
                    "Power Electronics" = "Power Electronics",
                    "PREDICTS" = "PREDICTS",
                    "PREDICTS 2" = "PREDICTS 2",
                    "Pre-Incubator" = "Pre-Incubator",
                    "PUC" = "PUC",
                    "PV Lifetime" = "PV Lifetime",
                    "PVMI" = "PVMI",
                    "PVRD SIPS" = "PVRD SIPS",
                    "PVRD" = "PVRD",
                    "PVRD2" = "PVRD2",
                    "Rooftop Solar Challenge" = "Rooftop Solar Challenge",
                    "Rooftop Solar Challenge 2" = "Rooftop Solar Challenge 2",
                    "RTC" = "RTC",
                    "RACER" = "RACER",
                    "SBIR/STTR FY11" = "SBIR/STTR FY11",
                    "SBIR/STTR FY12" = "SBIR/STTR FY12",
                    "SBIR/STTR FY13" = "SBIR/STTR FY13",
                    "SBIR/STTR FY14" = "SBIR/STTR FY14",
                    "SBIR/STTR FY15" = "SBIR/STTR FY15",
                    "SBIR/STTR FY16" = "SBIR/STTR FY16",
                    "SBIR/STTR FY17" = "SBIR/STTR FY17",
                    "SBIR/STTR FY18" = "SBIR/STTR FY18",
                    "SBIR/STTR FY19" = "SBIR/STTR FY19",
                    "SBIR/STTR FY20" = "SBIR/STTR FY20",
                    "SBIR/STTR FY21 PI R2" = "SBIR/STTR FY21 PI R2",
                    "SBV-1" = "SBV-1",
                    "SBV-2" = "SBV-2",
                    "SBV-3" = "SBV-3",
                    "SEEDS" = "SEEDS",
                    "SEEDS2-SES" = "SEEDS2-SES",
                    "SEGIS-AC" = "SEGIS-AC",
                    "SEIN" = "SEIN",
                    "SETO FY2018" = "SETO FY2018",
                    "SETO FY2019" = "SETO FY2019",
                    "SETO FY2020" = "SETO FY2020",
                    "SHINES" = "SHINES",
                    "Soft BOS" = "Soft BOS",
                    "Solar America Cities" = "Solar America Cities",
                    "Solar Forecasting" = "Solar Forecasting",
                    "SolarOps" = "SolarOps",
                    "SolarMat" = "SolarMat",
                    "SolarMat 2" = "SolarMat 2",
                    "Solar Market Pathways" = "Solar Market Pathways",
                    "SPARC" = "SPARC",
                    "STEP" = "STEP",
                    "SolWEB" = "SolWEB",
                    "SunPath" = "SunPath",
                    "SunShot Prize" = "SunShot Prize",
                    "SuNLaMP" = "SuNLaMP",
                    "SUNRISE" = "SUNRISE",
                    "T2M 1" = "T2M 1",
                    "T2M 2" = "T2M 2",
                    "T2M 3" = "T2M 3",
                    "TCF FY16" = "TCF FY16",
                    "TCF FY17" = "TCF FY17",
                    "TCF FY18" = "TCF FY18",
                    "TCF FY19" = "TCF FY19",
                    "TCF FY20" = "TCF FY20",
                    "TCF FY21" = "TCF FY21",	
                    "Thermal Storage" = "Thermal Storage",
                    "VELOCITI" = "VELOCITI"
					),
        selected = "All")
		
      ),
    
    mainPanel(
      leafletOutput("USA")
    )
  )
  
  
  
)
```

```{r, message = FALSE, warning = FALSE, error=FALSE, echo=FALSE}

# DEFINE SERVER LOGIC ---------------------------------------------------------------
server <- function(input, output) {
  
  output$USA <- renderLeaflet({
    df_leaf <-
      df %>%
      filter(Status == input$Status,
             FOA_Acronym == input$FOA_Acronym,
			       SUBPROGRAM == input$SUBPROGRAM)
    #write.csv(df_leaf, file="df_leaf.csv", row.names = FALSE)
    leaflet(df_leaf) %>%
      addProviderTiles(providers$CartoDB.Positron) %>%
      addMarkers(~Longitude,~Latitude,popup = ~Status,clusterOptions = markerClusterOptions())%>%
	    addMarkers(~Longitude,~Latitude,popup = ~FOA_Acronym,clusterOptions = markerClusterOptions())%>%
      addMarkers(~Longitude,~Latitude,popup = ~SUBPROGRAM,clusterOptions = markerClusterOptions())%>%
      addSearchOSM() %>%
      addMiniMap()     
    
  })
  
}
```

```{r, message = FALSE, warning = FALSE, error=FALSE, echo=FALSE}

shinyApp(ui = ui, server = server)


```
